\documentclass{article}
\usepackage{geometry}
\usepackage{xeCJK}
\setCJKmainfont{Source Han Serif CN}

\title{Schizophrenia vs schizoaffective disorder}
\author{M6 Clerk 何震邦}

\begin{document}
\maketitle
\section{Schizophrenia spectrum}
\begin{itemize}
    \item Schizophrenia
    \item Schizoaffective disorder
    \item Substance/medication-induced psychotic disorder
    \item Psychotic disorder due to another medical condition
\end{itemize}

\section{Diagnostic criteria}
\renewcommand{\theenumi}{\Alph{enumi}}
\renewcommand{\theenumii}{\arabic{enumii}}
\subsection{Schizophrenia}
\begin{enumerate}
    \item 2+ of the acute-phase symptoms, each present for a significant
        portion of time during a 1-month period (or less if successfully
        treated).  At least one of these must be (1), (2), or (3).
        \begin{enumerate}
            \item Delusions.
            \item Hallucinations.
            \item Disorganized speech.
            \item Grossly disorganized or catatonic behavior.
            \item Negative symptoms.
        \end{enumerate}
    \item For a significant portion of the time since the onset of the
        disturbance, level of functioning in 1+ major areas, such
        as work, interpersonal relations, or self-care, is markedly below
        the level achieved prior to the onset.
    \item Continuous signs of the disturbance persist for 6+ months. This
        6-month period must include 1+ month of symptoms (...) that meet
        Criterion A. ....
    \item (Rule out schizoaffective disorder.)
    \item The disturbance is not attributable to the physiological effects
        of a substance or another medical condition.
    \item If there is a history of autism spectrum disorder or a
        communication disorder of child­ hood onset, the additional diagnosis
        of schizophrenia is made only if prominent delusions or
        hallucinations, in addition to the other required symptoms of
        schizophrenia, are also present for 1+ month (...).
\end{enumerate}

\subsection{Schizoaffective disorder}
\begin{enumerate}
    \item An uninterrupted period of illness during which there is a major
        mood episode concurrent with Criterion A of schizophrenia.
    \item Delusions or hallucinations for 2 or more weeks in the absence of
        a major mood episode during the lifetime duration of the illness.
    \item Symptoms that meet criteria for a major mood episode are present
        for the majority of the total duration of the active and residual
        portions of the illness.
    \item The disturbance is not attributable to the effects of a substance
        or another medical condition.
\end{enumerate}
\end{document}
